---
title: "Assignment 4"
output: html_document
date: "2023-08-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Part 1 (Done in Latex)

Typeset the following equation:

Note: HTML makes the equation look weird but it is correct if you run the .rmd file

$$ f(x) = \frac{1}{\sqrt[3]{x^2+2x+5}} $$

```{r }
#Completed
```

## Part 2

Create a function which calculates the equation from part 1. Using base R, plot your function over the values of x ranging from -100 to 100. Make sure to label the y-axis using proper LaTeX notation for f(x) as generated in part 1 

```{r}
myFunction <- function(x) {
  a = x^2
  1 / (a +  2*x + 5)^(1/3)

}

# Set the domain
x <- seq(from = -100,to = 100, length.out = 10000)
length(x)

# Calculate f(x) over domain x
y <- myFunction(x)

plot(x,y,type = 'l', ylab = "f(x)") #l = line

#To add LaTeX notation
#install.packages('latex2exp')
library(latex2exp)

axis <- TeX(r'($f(x) =\frac{1}{\sqrt[3]{x^2+2x+5}}$)')
plot(x,y,type = 'l', ylab = axis) #l = line

```


## Part 3

Add noise, as discussed in class, using a function of your choice to f(x) and replot.

```{r }
#Source: Mathfor Data Analytics II lecture

# Calculate noise parameter following a uniform distribution
noise <- runif(n = length(x),min = 0,max = 0.05)
# Re-calculate f(x) with a noise parameter
y <- myFunction(x) + noise

# Plot f(x) with noise
#plot(x,y,type = "l", ylab = "f(x)")
plot(x,y,type = 'l', ylab = axis)
```

## Testing various equations (Please ignore)

```{r }
myFunction(2)
```



```{r }

myFunction <- function(x) {
  y = 2*x
  y * 2
}
```

```{r }
myFunction(2)

```


```{r }
myFunction <- function(x) {
  a = x^2
  b = 2*x
  c = a + b + 5
  d = 1 / (c)^(1/3)
}

```

```{r }
myFunction(2)
```


```{r }
myFunction <- function(x) {
  a = x^2
  1 / (a +  2*x + 5)^(1/3)
}
```


```{r }
myFunction(2)
```
